Word Sense Disambiguation\\ \small{Leveraging the NLTK Toolkit and External Tools}

### 2011-04-14 paper/paper.tex
Merged the discarded collocation section with the original
paper captions

\begin{figure}[H]
\includegraphics[width=\textwidth]{pg_0004}
\caption{\label{fig4}}
\end{figure}

@@

We ran two baselines, one with each machine learning algorithm:

\begin{tabular}{l l | r r r}
& grain& precision& recall& attempted\\
\hline
\multirow{3}{*}{\Naive{} Bayes} &
coarse  &  0.737 & 0.379 &   51.39\\
&mixed  &  0.730 & 0.375 &   51.39\\
& fine  &  0.693 & 0.356 &   51.39\\
\multirow{3}{*}{Decision Tree} &
coarse  &  0.612 & 0.612 &  100.00\\
&mixed  &  0.594 & 0.594 &  100.00\\
& fine  &  0.552 & 0.552 &  100.00\\
\end{tabular}

>>>>

\begin{figure}[H]
\includegraphics[width=\textwidth]{pg_0004}
\caption{\label{fig4}The scores of systems with colocation window between 2 and 4, cooccurrence handling on, \naive{} Bayes classifier and dependency parsing off are presented here. Each plotted number corresponds to a system, and the number refers to the colocation window}
\end{figure}

@@

We ran two baselines, one with each machine learning algorithm (table \ref{tab:base} and figure \ref{fig:base}).

\begin{table}
\begin{tabular}{l l | r r r}
& grain& precision& recall& attempted\\
\hline
\multirow{3}{*}{\Naive{} Bayes} &
coarse  &  0.737 & 0.379 &   51.39\\
&mixed  &  0.730 & 0.375 &   51.39\\
& fine  &  0.693 & 0.356 &   51.39\\
\multirow{3}{*}{Decision Tree} &
coarse  &  0.612 & 0.612 &  100.00\\
&mixed  &  0.594 & 0.594 &  100.00\\
& fine  &  0.552 & 0.552 &  100.00\\
\end{tabular}
\caption{\label{tab:base}Scores for the baseline system}
\end{table}
